A 38 Million Year Old Mini-Neptune in the Kepler Field

### 2021-09-22 paper/ms.tex
update ms

% 208 words (250 max)
\begin{abstract}
  Kepler\,1627A is a G8V star previously known to host a
  $3.3\,R_\oplus$ mini-Neptune on a 7.2\,day orbit.  The star was
  observed by the Kepler space telescope because it is nearby
  ($d=329\pm3\,{\rm pc}$) and it resembles the Sun.  Here we show
  using Gaia kinematics, TESS stellar rotation periods, and
  spectroscopic lithium abundances that Kepler\,1627 is a member of
  the \clusterage\ old $\delta$~Lyr cluster.  To our knowledge,
  Kepler\,1627Ab is the youngest planet with a precise age yet found
  by the main Kepler mission.  From unresolved starspot-crossing
  events in the Kepler photometry and a Keck/HIRES transit we find
  that the planet is likely on a prograde orbit.  We also briefly
  explore the flare arrival time distribution in the short cadence
  Kepler photometry.  The $\delta$~Lyr cluster is one of many stellar
  groups whose properties have been clarified using Gaia; many other
  exoplanet hosts belong to these new clusters.  Verifying the results
  of Gaia clustering analyses using TESS rotation periods offers a
  promising path toward expanding the census of age-dated planets, and
  our corresponding understanding of planetary evolution.
\end{abstract}

@@

The K2 and TESS missions have now enabled the detection of about ten
close-in planets younger than 100 million years, all smaller than
Jupiter
\citep{Mann_K2_33b_2016,David_et_al_2017,david_four_2019,newton_tess_2019,bouma_cluster_2020,plavchan_planet_2020,rizzuto_tess_2020,martioli_aumicbc_2021}.
The Kepler mission however has not yielded any planets with precise
ages below one gigayear \citep{Meibom_et_al_2013}.  The reason is that
during the main Kepler mission (2009--2013), only four open clusters
were known in the Kepler field,
%: NGC\,6866, NGC\,6811, NGC\,6819, and NGC\,6791,
with ages spanning 0.7\,Gyr to 9\,Gyr
\citep{meibom_kepler_2011}.  Though isochronal, gyrochronal, and lithium-based
analyses suggest that younger Kepler planets do exist
\citep{berger_identifying_2018,david_sizes_2021}, accurate and precise
age measurements typically require an ensemble of stars.  Fortunately,
recent analyses of the kinematic, photometric, and astrometric Gaia
data have since expanded our knowledge of cluster memberships
\citep[{\it
e.g.},][]{cantatgaudin_gaia_2018,zari_3d_2018,kounkel_untangling_2019,Meingast2021,Kerr2021}.
As part of our Cluster Difference Imaging Photometric Survey (CDIPS,
\citealt{bouma_cdipsI_2019}), we concatenated the available analyses
from the literature, which yielded a list of candidate young and
age-dated stars (see Appendix~\ref{app:targetlist}).

@@

Comparing our young star list against the Kepler field yielded two
discoveries.  The first, to be discussed in an upcoming analysis by
J.~Curtis et al{.}, is that Kepler observed the $\approx$350\,Myr open
cluster Theia~520 (UBC~1).  At least six Kepler planets are known in
the cluster from the Kepler-52 and Kepler-968 systems
\citep{rowe_validation_2014,jontof-hutter_following_2021}.  The second
discovery, and the focus of this work, is that Kepler observed a
portion of the $\delta$\,Lyr cluster (Stephenson-1; Theia~73;
\citealt{stephenson_possible_1959}).  Figure~\ref{fig:skychart} shows
the overlap between the Kepler field and the cluster.

@@

Beyond the kinematic and rotational lines of evidence for the youth of
\sn, there is a final consistency check: the abundance of
Li\,\textsc{I} as inferred from the 6708\,\AA\ doublet \citep[{\it
e.g.},][]{soderblom_ages_2014}.  We acquired an iodine-free spectrum
from Keck/HIRES on the night of 2021 March 26 using the standard setup
and reduction techniques of the California Planet Survey
\citep{howard_cps_2010}.  Following the equivalent width measurement
procedure described by \citet{bouma_2021_ngc2516}, we find ${\rm
EW}_{\rm Li} = 233^{+5}_{-7}$\,m\AA.   %Note that this value does not
%correct for the Fe\,\textsc{I} blend at 6707.44\AA. 
Given the effective temperature of \sn\ (Table~\ref{tab:starparams}),
this measurement is also in line with expectations for a 38\,Myr star
({\it e.g.}, \citealt{randich_gaiaeso_2018};
\citealt{bouma_2021_ngc2516}).

@@

		\subfloat{
			\includegraphics[width=0.5\textwidth]{f5a.pdf}
			\includegraphics[width=0.5\textwidth]{f5b.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
  \caption{ {\bf The light curve of Kepler\,1627.}
    {\it Top}: 
    The Kepler data span 1{,}437 days (3.9 years), sampled at
    30 minute cadence;  a 100 day segment is shown.  The
    top panel shows the \texttt{PDCSAP} median-subtracted flux in
    units of parts-per-thousand ($\times 10^{-3}$).  The dominant
    signal is induced by starspots.  The stellar
    variability model (orange line) is subtracted below, revealing the
    transits of \pn, as well as other deviations from the model.  The
    online Figure Set spans the entire 3.9 years of observations.
    {\it Bottom}:
    Phase-folded transit of Kepler 1627Ab with stellar variability
    removed.  Windows over 20 hours ({\it left}) and the entire orbit
    ({\it right}) are shown.  The 2-$\sigma$ uncertainties and the
    maximum best-fit model are the faint purple band, and the dark
    purple line.  Gray points are individual flux measurements; black
    points bin these every 20 minutes, and have a representative error bar
    shown.  The asymmetric residual during transit appears to be robust when using
    different
    detrending methods.
    \label{fig:lc}
  }
\end{figure*}

@@

		\subfloat{
			\includegraphics[width=0.49\textwidth]{f16.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Evidence for a prograde orbit of Kepler 1627 Ab.}
    {\it Top:} 
    The time of each Kepler transit was measured, along with the local
    slope of the light curve.  The two quantities appear
    anti-correlated, which is most easily explained by starspot
    crossings during the first (second) half of transit inducing a
    positive (negative) TTV, provided that the orbit is prograde
    \citep{mazeh_time_2015}.  The units along the abscissa are most
    easily understood by considering that the stellar flux changes by
    $\sim$60\,ppt per half rotation period
    ($\sim$1.3\,days).
    {\it Bottom:} Radial velocities acquired using Keck/HIRES during
    the transit of 2021 Aug 7, observed simultaneously with MuSCAT3.
    The best-fit sky-projected obliquity for this model is listed in
    red.  While the intra-exposure RV scatter precludes a detection of
    the RM effect, the photometric transit depths are consistent
    across the {\it griz} bandpasses.
    \label{fig:obliquity}
	}
\end{figure}
\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.8\textwidth]{f14.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Radii, orbital periods, and ages of transiting exoplanets}.
    %Planets older than $10^9$ years are shown with gray markers.
    Planets younger than a gigayear with ${\rm \tau}/\sigma_{\rm \tau}
    > 3$ are emphasized, for $\tau$ the age.  \pn\ is shown with a
    star.  The large sizes of the youngest transiting planets could be
    explained by their primordial atmospheres not yet having
    evaporated; direct measurements of the atmospheric outflows or
    planetary masses would help to confirm this expectation.
    Selection effects may also be important.  Parameters are from the
    NASA Exoplanet Archive (2021 Sept 15).
		\label{fig:rp_period_age}
	}
\end{figure*}

@@

If the \pn\ transit signal is created by a genuine planet,  then to
our knowledge its age would make it the youngest planet yet found by
the main Kepler mission.\footnote{The re-purposed K2 mission however
has found two younger systems containing five planets: K2-33b
($9\pm1\,{\rm Myr}$; \citealt{Mann_K2_33b_2016,David_et_al_2017}) and
V1298 Tau ($23\pm4\,{\rm Myr}$; \citealt{david_four_2019}).}  The light
curve and the phase-folded transit are shown in
Figure~\ref{fig:lc}.  The photometry is dominated by a
quasi-periodic starspot signal with a peak-to-peak amplitude that
varies between 2\% and 8\%.  The signal
repeats every $2.642\pm0.042$\,days, where the quoted uncertainty is based on
the scatter in rotation periods measured from each individual Kepler quarter. 
Our model for the starspot signal is discussed in detail
in Appendix~\ref{app:gptransit}, and the adopted stellar
parameters are listed in Table~\ref{tab:starparams}.  The stellar mass,
radius, and effective temperature are found by interpolating against a
38$\,$Myr MIST isochrone.  The systematic uncertainties are taken
to be the difference between the PARSEC and MIST isochrones, and the
reported uncertainties are a quadrature sum of the statistical and
systematic components. 
The transit fitting results, given in
Table~\ref{tab:posterior}, are consistent with a mini-Neptune sized
planet ($3.34\pm 0.18\,R_\oplus$) on a close-in circular\footnote{Our
transit fitting yields $e<0.48$ at 2-$\sigma$; the constraints on the
eccentricity are not particularly strong.} orbit around a G8V star
($0.88 \pm 0.02 R_\odot$).

@@

The second line of confirmatory evidence comes by analyzing the
individual Kepler transit times. We isolated each of the 144 observed
transits to within $\pm4.5$\,hr of each transit, and fitted each
window with both {\it i)} a local second-order polynomial and transit,
and {\it ii)} a local linear trend.  We let the mid-time of each
transit float, and then calculated the residual between the measured
mid-time and that of a periodic orbit.  This residual, the transit
timing variation (TTV), is plotted in Figure~\ref{fig:obliquity}
against the local linear slope.  A significant correlation of $-0.0564
\pm 0.0098\ {\rm ppt\,day}^{-1}$ is observed.  Less than ten Kepler
Objects of Interest have shown this correlation
\citep{holczer_time_2015}, which is most readily interpreted as a TTV
induced by unresolved starspot crossings \citep{mazeh_time_2015}.
This is only possible if the planet transits the primary star, which
excludes a background eclipsing binary scenario, and therefore
confirms that \pn\ is a planet.  It also implies that the planet's
orbit is prograde.  The latter interpretation assumes that the
dominant photometric variability is induced by dark spots, rather than
bright faculae.  Given the observed transition of Sun-like stellar
variability from spot to faculae-dominated regimes, we expect this
inference to be reasonably secure
\citep{shapiro_are_2016,montet_long-term_2017,reinhold_stellar_2020}.

A third supporting line of evidence for the planetary interpretation
also exists, though we consider it less definitive than the stellar
density and TTV-local slope correlation.  We observed a transit of
\pn\ on the night of 2021 Aug 7 simultaneously with Keck/HIRES and
MuSCAT3.  We scheduled the observations using the ephemeris of
\citet{holczer_transit_2016}.  Although we did not detect the
Rossiter-McLaughlin (RM) anomaly, the multi-band MuSCAT3 light curves
show the transit, and it appears to be achromatic
(Figure~\ref{fig:obliquity}, lower panels).  Fitting the MuSCAT3
photometry with a model that lets the transit depths vary across
bandpasses, we find {\it griz} depths consistent with the Kepler depth
at 0.6, 0.3, 0.3, and 1.1-$\sigma$ respectively.  The MuSCAT3
observations also suggest a transit duration $17.4\pm3.6\,{\rm
minutes}$ shorter than the Kepler transits; further photometric
follow-up could help confirm whether such changes are indeed
happening.  For the RM analysis, the details are discussed in
Appendix~\ref{app:rm}.  While our RM data are marginally more
consistent with a prograde or polar orbit than a retrograde orbit,
the expected velocity anomaly ($\Delta v_{\rm RM}\approx
20\,{\rm m\,s}^{-1}$) is a factor of two smaller than the
spot-corrected exposure-to-exposure scatter.  We are therefore not in
a position to claim a spectroscopic detection of the RM effect, nor a
precise quantification of the stellar obliquity.

@@

Kepler\,1627Ab provides a new extremum in the ages of the Kepler
planets, and opens multiple avenues for further study.  Further
observations of spectroscopic transits could yield a more precise
stellar obliquity, and could confirm or refute the expected prograde
orbital geometry.  Similarly, transit spectroscopy aimed at detecting
outflows of hydrogen or helium could yield insight into the
evolutionary state of the atmosphere
\citep{spake_helium_2018,vissapragada_2020}.  Determining the precise
amount of high-energy irradiation incident on the planet would also
help in clarifying the expected outflow rate \citep[{\it
e.g.},][]{poppenhaeger_2021}.  Finally, a challenging but informative
quantity to measure would be the planet's mass.  This might be
possible through long-term monitoring of the transit times and
durations, or through a high-cadence multi-color radial velocity
campaign.  Measured at sufficient precision, the mass could yield
constraints on both the planet's composition and its initial entropy
\citep{owen_constraining_2020}.

Separately, the Kepler data may yet contain further information.
Although our transit timing study did not yield the detection of any
planet-induced transit timing or duration variations,
Appendix~\ref{app:flare} highlights an odd flare timing coincidence
that may be suggestive of star-planet interactions.  We encourage its
exploration by investigators more versed in the topic than ourselves.

In the context of the transiting planet population, \pn\ is among the
youngest known (Figure~\ref{fig:rp_period_age}).  Comparable systems
with precise ages below 100\,Myr include K2-33, DS~Tuc, HIP~67522,
TOI~837, the two-planet AU~Mic system, and the four-planet V1298~Tau
system
\citep{Mann_K2_33b_2016,David_et_al_2017,newton_tess_2019,david_four_2019,bouma_cluster_2020,plavchan_planet_2020,martioli_aumicbc_2021}.
\pn\ is one of the smallest planets in this sample ($3.34\pm
0.18\,R_\oplus$), which could be linked to the selection effects
imposed by the spot-induced photometric variability at very young ages
\citep[{\it e.g.},][]{zhou_2021_tois}.  Assuming that these young
planets have masses between $\approx$5$\,M_\oplus$ and 10$\,M_\oplus$,
their large sizes and presumed low densities would be in accord with
the expectation that mini-Neptunes start their lives with large
primordial atmospheres that are shed over the first gigayear
\citep{Owen_Wu_2013,Fulton_et_al_2017,ginzburg_corepowered_2018}.  Our
suggestion of a prograde is consistent with a quiescent
disk-driven migration history, and differs from misalignments that
have been observed for some older
mini-Neptunes~\citep{sanchis-ojeda_starspots_2011,albrecht_obliquities_2012,dalal_2019_hd3167,rubenzahl_tess-keck_2021}.
Spectroscopic follow-up observations of the transit remain necessary
however to verify whether the TTV-slope correlation is yielding the
correct orbital geometry.

@@

Ultimately, the main advance of this work is a precise measurement of
the age of \pn.   This age measurement was enabled by identifying the
connection of the star to the \cn\ using the Gaia data.
Table~\ref{tab:v06} should enable similar cross-matches to already
known planets, as well as forthcoming planets from the TESS mission
\citep{ricker_transiting_2015,guerrero_tess_2021}.  An alternative
approach for age-dating more planets could be to identify kinematic
associations around known exoplanet host stars using positions and
tangential velocities from Gaia, and to then verify these associations
with ancillary rotation periods and spectroscopy \citep[{\it
e.g.},][]{tofflemire_tess_2021}.

@@

Figure~\ref{fig:lc} shows the resulting model in orange (top) and
purple (bottom).  While the fit appears reasonably good, an asymmetry
is present during the transit: the measured flux is systematically
high during the first half, and low in the second half.  To determine
whether this effect was not caused by our stellar variability model, we 
explored an alternative approach in which we isolated each transit
window and locally fitted out polynomial trends, and then binned all
the observed transits; the asymmetry was still present, at a
comparable amplitude.

Figures~\ref{fig:phasequarter} and~\ref{fig:phaseyear} show the
Kepler data binned over quarters and years.  In
Figure~\ref{fig:phasequarter}, Quarter 6 shows the strongest asymmetry
out of the quarters: a deviation of about 3\,ppt from
expectation.  Quarter 7 shows an anomaly at roughly the same transit
phase.  Year 2 correspondingly shows the strongest anomaly out of any
year in Figure~\ref{fig:phaseyear}.

We considered three possible explanations for the anomaly: gravity
darkening, transit timing variations, and spot-crossing events.
Gravity darkening is based on the premise that the rapidly rotating
star becomes oblate, and brighter near the poles than the equator
\citep[{\it e.g.},][]{masuda_spin-orbit_2015}.  The fractional shape
change due to gravity darkening is on the order of $(P_{\rm
break}/P_{\rm rot})^2$, for $P_{\rm break}$ the break-up rotation
period, and $P_{\rm rot}$ the rotation period.  Using the parameters
from Table~\ref{tab:posterior}, this yields an expected 1.4\%
distortion of the $\approx$1.8\,ppt transit depth: {\it i.e.}, an
absolute deviation of $\approx$2.5\,ppm.  The observed residual has a
semi-amplitude of $\approx 50\,{\rm ppm}$.  Since the expected signal is
smaller than the observed anomaly by over an order of magnitude, gravity
darkening seems to be an unlikely explanation.

The scenario of transit timing variations (TTVs) producing the
asymmetry seems unlikely, since the analysis by
\citet{holczer_transit_2016} implies that any such variations in \sn\
need to be less than of order minutes.  
Our independent TTV analysis found similar results.
Figures~\ref{fig:phasequarter}
and~\ref{fig:phaseyear} also provide little evidence in support of
this possibility.

>>>>

% 208 words (250 max)
\begin{abstract}
  Kepler\,1627A is a G8V star previously known to host a
  $3.3\,R_\oplus$ mini-Neptune on a 7.2\,day orbit.  The star was
  observed by the Kepler space telescope because it is nearby
  ($d=329\pm3\,{\rm pc}$) and it resembles the Sun.  Here we show
  using Gaia kinematics, TESS stellar rotation periods, and
  spectroscopic lithium abundances that Kepler\,1627 is a member of
  the \clusterage\ old $\delta$~Lyr cluster.  To our knowledge,
  Kepler\,1627Ab is the youngest planet with a precise age yet found
  by the main Kepler mission.  From unresolved starspot-crossing
  events in the Kepler photometry and a Keck/HIRES transit we find
  that the planet is likely on a prograde orbit.  The average Kepler
  transit profile also appears asymmetric; our current best
  explanation is that of a dusty atmospheric outflow being present,
  but this remains to be confirmed.  Broadly speaking, the
  $\delta$~Lyr cluster is one of many stellar groups whose properties
  have been clarified using Gaia; many other exoplanet hosts belong to
  these new clusters.  Verifying the results of Gaia clustering
  analyses using TESS rotation periods offers a promising path toward
  expanding the census of age-dated planets, and our corresponding
  understanding of planetary evolution.
\end{abstract}

@@

The K2 and TESS missions have now enabled the detection of about ten
close-in planets younger than 100 million years, all smaller than
Jupiter
\citep{Mann_K2_33b_2016,David_et_al_2017,david_four_2019,newton_tess_2019,bouma_cluster_2020,plavchan_planet_2020,rizzuto_tess_2020,martioli_aumicbc_2021}.
The Kepler mission however has not yielded any planets with precise
ages below one gigayear \citep{Meibom_et_al_2013}.  The reason is that
during the main Kepler mission (2009--2013), only four open clusters
were known in the Kepler field,
%: NGC\,6866, NGC\,6811, NGC\,6819, and NGC\,6791,
with ages spanning 0.7\,Gyr to 9\,Gyr
\citep{meibom_kepler_2011}.  Though isochronal, gyrochronal, and lithium-based
analyses suggest that younger Kepler planets do exist
\citep{berger_identifying_2018,david_sizes_2021}, accurate and precise
age measurements typically require an ensemble of stars.  Fortunately,
recent analyses of the Gaia
data have since expanded our knowledge of cluster memberships
\citep[{\it
e.g.},][]{cantatgaudin_gaia_2018,zari_3d_2018,kounkel_untangling_2019,Meingast2021,Kerr2021}.
As part of our Cluster Difference Imaging Photometric Survey (CDIPS,
\citealt{bouma_cdipsI_2019}), we concatenated the available analyses
from the literature, which yielded a list of candidate young and
age-dated stars (see Appendix~\ref{app:targetlist}).

@@

Matching our young star list against stars observed by Kepler yielded
two discoveries.  The first, to be discussed in an upcoming analysis
by J.~Curtis et al{.}, is that Kepler observed the $\approx$350\,Myr
open cluster Theia~520 (UBC~1).  At least six Kepler planets are known
in the cluster from the Kepler-52 and Kepler-968 systems
\citep{rowe_validation_2014,jontof-hutter_following_2021}.  The second
discovery, and the focus of this work, is that Kepler observed a
portion of the $\delta$\,Lyr cluster (Stephenson-1; Theia~73;
\citealt{stephenson_possible_1959}).  Figure~\ref{fig:skychart} shows
the overlap between the Kepler field and the cluster.

@@

Beyond the kinematic and rotational lines of evidence for the youth of
\sn, there is a final consistency check: the abundance of
Li\,\textsc{I} as inferred from the 6708\,\AA\ doublet \citep[{\it
e.g.},][]{soderblom_ages_2014}.  We acquired an iodine-free spectrum
from Keck/HIRES on the night of 2021 March 26 using the standard setup
and reduction techniques of the California Planet Survey
\citep{howard_cps_2010}.  Following the equivalent width measurement
procedure described by \citet{bouma_2021_ngc2516}, we find ${\rm
EW}_{\rm Li} = 233^{+5}_{-7}$\,m\AA.   %Note that this value does not
%correct for the Fe\,\textsc{I} blend at 6707.44\AA. 
Given the effective temperature of \sn\ (Table~\ref{tab:starparams}),
this measurement is also in line with expectations for a 38\,Myr star
({\it e.g.}, \citealt{randich_gaiaeso_2018};
\citealt{bouma_cluster_2020}).

@@

		\subfloat{
			\includegraphics[width=0.5\textwidth]{f5a.pdf}
			\includegraphics[width=0.5\textwidth]{f5b.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
  \caption{ {\bf The light curve of Kepler\,1627.}
    {\it Top}: 
    The Kepler data span 1{,}437 days (3.9 years), sampled at
    30 minute cadence;  a 100 day segment is shown.  The
    top panel shows the \texttt{PDCSAP} median-subtracted flux in
    units of parts-per-thousand ($\times 10^{-3}$).  The dominant
    signal is induced by starspots.  The stellar
    variability model (orange line) is subtracted below, revealing the
    transits of \pn.  The
    online Figure Set spans the entire 3.9 years of observations.
    {\it Bottom}:
    Phase-folded transit of Kepler 1627Ab with stellar variability
    removed.  Windows over 20 hours ({\it left}) and the entire orbit
    ({\it right}) are shown.  The 2-$\sigma$ model uncertainties and
    the best-fit model are the light purple band and the dark purple
    line.  Gray points are individual flux measurements; black points
    bin these to 20 minute intervals, and have a representative
    1-$\sigma$ error bar in the lower right of each panel.  The
    asymmetric residual during transit appears to be robust to
    different detrending methods.
    \label{fig:lc}
  }
\end{figure*}

@@

		\vspace{-0.1cm}
		\subfloat{
			\includegraphics[width=0.49\textwidth]{f16.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Evidence for a prograde orbit of Kepler 1627 Ab.}
    {\it Top:} 
    The time of each Kepler transit was measured, along with the local
    slope of the light curve.  The two quantities appear
    anti-correlated, which is most easily explained by starspot
    crossings during the first (second) half of transit inducing a
    positive (negative) TTV, provided that the orbit is prograde
    \citep{mazeh_time_2015}.  The units along the abscissa are most
    easily understood by considering that the stellar flux changes by
    $\sim$60\,ppt per half rotation period ($\sim$1.3\,days).
    {\it Bottom:}
    Radial velocities acquired using Keck/HIRES during the transit of
    2021 Aug 7, observed simultaneously with MuSCAT3.  Shaded bands
    show 2-$\sigma$ model uncertainties.  The photometric transit
    depths are consistent across the {\it griz} bandpasses.  The
    best-fitting model including the RM effect and a quadratic trend
    in time is shown with the red line.  The radial velocity scatter
    between exposures prevents a significant detection of the RM
    effect.
    \label{fig:obliquity}
	}
\end{figure}
\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.8\textwidth]{f14.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Radii, orbital periods, and ages of transiting exoplanets}.
    %Planets older than $10^9$ years are shown with gray markers.
    Planets younger than a gigayear with ${\rm \tau}/\sigma_{\tau} >
    3$ are emphasized, where $\tau$ is the age and $\sigma_{\tau}$ is
    its uncertainty.  \pn\ is shown with a star.  The large sizes of
    the youngest transiting planets could be explained by their
    primordial atmospheres not yet having evaporated; direct
    measurements of the atmospheric outflows or planetary masses would
    help to confirm this expectation.  Selection effects may also be
    important.  Parameters are from the NASA Exoplanet Archive (2021
    Sept 15).
		\label{fig:rp_period_age}
	}
\end{figure*}

@@

If the \pn\ transit signal is created by a genuine planet,  then to
our knowledge its age would make it the youngest planet yet found by
the main Kepler mission.\footnote{The re-purposed K2 mission however
has found two younger systems containing five planets: K2-33b
($9\pm1\,{\rm Myr}$; \citealt{Mann_K2_33b_2016,David_et_al_2017}) and
V1298 Tau ($23\pm4\,{\rm Myr}$; \citealt{david_four_2019}).}  The light
curve and the phase-folded transit are shown in
Figure~\ref{fig:lc}.  The photometry is dominated by a
quasi-periodic starspot signal with a peak-to-peak amplitude that
varies between 2\% and 8\%.  The signal
repeats every $2.642\pm0.042$\,days, where the quoted uncertainty is based on
the scatter in rotation periods measured from each individual Kepler quarter. 
Our model for the starspot signal is discussed in detail
in Appendix~\ref{app:gptransit}, and the adopted stellar
parameters are listed in Table~\ref{tab:starparams}.  The stellar mass,
radius, and effective temperature are found by interpolating against a
38$\,$Myr MIST isochrone.  Their systematic uncertainties are taken
to be the difference between the PARSEC and MIST isochrones, and the
reported uncertainties are a quadrature sum of the statistical and
systematic components. 
The transit fitting results, given in
Table~\ref{tab:posterior}, are broadly consistent with a mini-Neptune sized
planet ($3.34\pm 0.18\,R_\oplus$) on a close-in circular\footnote{Our
transit fitting yields $e<0.48$ at 2-$\sigma$; the constraints on the
eccentricity are not particularly strong.} orbit around a G8V star
($0.88 \pm 0.02 R_\odot$).

@@

The second line of confirmatory evidence comes by analyzing the
individual Kepler transit times. We isolated each of the 144 observed
transits to within $\pm4.5$\,hr of each transit, and fitted each
window with both {\it i)} a local second-order polynomial and transit,
and {\it ii)} a local linear trend.  We let the mid-time of each
transit float, and then calculated the residual between the measured
mid-time and that of a periodic orbit.  This residual, the transit
timing variation (TTV), is plotted in Figure~\ref{fig:obliquity}
against the local linear slope.  A significant correlation of $-0.0564
\pm 0.0098\ {\rm ppt\,day}^{-1}$ is observed.  Fewer than ten Kepler
Objects of Interest have shown this correlation
\citep{holczer_time_2015}, which is most readily interpreted as a TTV
induced by unresolved starspot crossings \citep{mazeh_time_2015}.
This is only possible if the planet transits the primary star, which
excludes a background eclipsing binary scenario, and therefore
confirms that \pn\ is a planet.  It also implies that the planet's
orbit is prograde.  The latter point assumes that the dominant
photometric variability is induced by dark spots, and not bright
faculae.  Given the observed transition of Sun-like stellar
variability from spot to faculae-dominated regimes, we expect this
assumption to be reasonably secure
\citep{shapiro_are_2016,montet_long-term_2017,reinhold_stellar_2020}.

A third supporting line of evidence for the planetary interpretation
also exists, though we consider it less definitive than the stellar
density and TTV-local slope correlation.  We observed a transit of
\pn\ on the night of 2021 Aug 7 simultaneously with Keck/HIRES and
MuSCAT3.  We scheduled the observations using the ephemeris of
\citet{holczer_transit_2016}.  Although we did not detect the
Rossiter-McLaughlin (RM) anomaly, the multi-band MuSCAT3 light curves
show the transit (Figure~\ref{fig:obliquity}, lower panels).  Fitting
the MuSCAT3 photometry with a model that lets the transit depths vary
across each bandpass, we find {\it griz} depths consistent with the
Kepler depth at 0.6, 0.3, 0.3, and 1.1-$\sigma$ respectively.  The
MuSCAT3 observations also suggest a transit duration $17.4\pm3.6\ {\rm
minutes}$ shorter than the Kepler transits; further photometric
follow-up could help confirm whether the transit duration is indeed
changing.  For our RM analysis, the details are discussed in
Appendix~\ref{app:rm}.  While the velocities are marginally more
consistent with a prograde or polar orbit than a retrograde orbit, the
spot-corrected exposure-to-exposure scatter ($\sigma_{\rm RV}\approx
50$\ms) is significantly larger than the expected velocity anomaly
($\Delta v_{\rm RM}\approx 20\,{\rm m\,s}^{-1}$).  We are therefore
not in a position to claim a spectroscopic detection of the RM effect,
nor a precise quantification of the stellar obliquity.

@@

Kepler\,1627Ab provides a new extremum in the ages of the Kepler
planets, and opens multiple avenues for further study.  Further
observations of spectroscopic transits could yield a quantification of
the stellar obliquity, and would confirm or refute the expected
prograde orbital geometry.  Similarly, transit spectroscopy aimed at
detecting atmospheric outflows could yield insight into the
evolutionary state of the atmosphere \citep[{\it
e.g.},][]{ehrenreich_giant_2015,spake_helium_2018,vissapragada_2020}.
Observations aimed at quantifying the amount of high-energy
irradiation incident on the planet would also help in clarifying the
expected outflow rate \citep[{\it e.g.},][]{poppenhaeger_2021}.
Finally, a challenging but informative quantity to measure would be
the planet's mass.  This might be possible through long-term
monitoring of the transit times and durations, or through a
high-cadence multi-color radial velocity campaign.  Measured at
sufficient precision, the mass could yield constraints on both the
planet's composition and its initial entropy
\citep{owen_constraining_2020}.

Separately, the Kepler data may yet contain additional information.
For instance, one possible explanation for the transit asymmetry shown
in Figure~\ref{fig:lc} is that of a dusty asymmetric outflow.  Other
possible explanations such as favored longitudes for starspot
crossings seem strained, for reasons discussed in
Appendix~\ref{app:gptransit}.  Dusty outflows are theoretically
expected for young mini-Neptunes, and the amplitude of the observed
asymmetry is also roughly consistent with predictions
\citep{wang_dai_2019}.  Beyond the planetary transits,
Appendix~\ref{app:flare} highlights a separate odd coincidence in the
Kepler data, in the arrival time distribution of stellar flares.  We
encourage its exploration by investigators more versed in the topic
than ourselves.

In the context of the transiting planet population, \pn\ is among the
youngest known (Figure~\ref{fig:rp_period_age}).  Comparable systems
with precise ages include K2-33, DS~Tuc, HIP~67522,
TOI~837, the two-planet AU~Mic system, and the four-planet V1298~Tau
system
\citep{Mann_K2_33b_2016,David_et_al_2017,newton_tess_2019,david_four_2019,bouma_cluster_2020,plavchan_planet_2020,martioli_aumicbc_2021}.
\pn\ is one of the smallest planets in this sample ($3.34\pm
0.18\,R_\oplus$), which could be linked to the selection effects
imposed by the spot-induced photometric variability at very young ages
\citep[{\it e.g.},][]{zhou_2021_tois}.  Assuming that these young
planets have masses between $\approx$5$\,M_\oplus$ and 10$\,M_\oplus$,
their large sizes and presumed low densities would be in accord with
the expectation that mini-Neptunes start their lives with large
primordial atmospheres that are shed over the first gigayear
\citep{Owen_Wu_2013,Fulton_et_al_2017,ginzburg_corepowered_2018}.  Our
suggestion of a prograde orbit is consistent with a quiescent
disk-driven migration history, and differs from misalignments that
have been observed for some older
mini-Neptunes~\citep{sanchis-ojeda_starspots_2011,albrecht_obliquities_2012,dalal_2019_hd3167,rubenzahl_tess-keck_2021}.
Spectroscopic follow-up observations of the transit remain necessary
however to verify whether the TTV-slope correlation is yielding the
correct orbital geometry.

@@

Ultimately, the main advance from this work is a precise measurement of
the age of \pn.   This measurement was enabled by identifying the
connection of the star to the \cn\ using Gaia kinematics, and then by
using the Gaia HR diagram and TESS stellar rotation periods to verify the
cluster's existence.
Table~\ref{tab:v06} should enable similar cross-matches to already
known planets, as well as forthcoming planets from TESS
\citep{guerrero_tess_2021}.  An alternative
approach for age-dating more planets could be to identify kinematic
associations around known exoplanet host stars using positions and
tangential velocities from Gaia, and to then verify these associations
with ancillary rotation periods and spectroscopy \citep[{\it
e.g.},][]{tofflemire_tess_2021}.

@@

Figure~\ref{fig:lc} shows the resulting model in orange (top) and
purple (bottom).  While the fit appears reasonably good, an asymmetry
is present during the transit: the measured flux is systematically
high during the first half, and low in the second half.  To determine
whether this effect was caused by our stellar variability model, we 
explored an alternative approach in which we isolated each transit
window and locally fitted out polynomial trends, and then binned all
the observed transits; the asymmetry was still present, at a
comparable amplitude.

Figures~\ref{fig:phasequarter} and~\ref{fig:phaseyear} show the Kepler
data binned over quarters and years.  In
Figure~\ref{fig:phasequarter}, Quarter 6 shows the strongest asymmetry
out of the quarters: a deviation of about 3\,ppt from expectation.
Quarter 7 shows an anomaly at roughly the same transit phase.  Year 2
correspondingly shows the strongest anomaly out of any year in
Figure~\ref{fig:phaseyear}; the asymmetry is visually apparent however
in each of Years 2, 3, and 4.

We therefore considered four possible explanations for the anomaly:
gravity darkening, transit timing variations, spot-crossing events,
and a persistent asymmetric dusty outflow.

Gravity darkening is based on the premise that the rapidly rotating
star is oblate, and brighter near the poles than the equator
\citep[{\it e.g.},][]{masuda_spin-orbit_2015}.  The fractional transit
shape change due to gravity darkening is on the order of $(P_{\rm
break}/P_{\rm rot})^2$, for $P_{\rm break}$ the break-up rotation
period, and $P_{\rm rot}$ the rotation period.  Using the parameters
from Table~\ref{tab:posterior}, this yields an expected 0.14\%
distortion of the $\approx$1.8\,ppt transit depth: {\it i.e.}, an
absolute deviation of $\approx$2.5\,ppm.  The observed residual has a
semi-amplitude of $\approx 50\,{\rm ppm}$.  Since the expected signal
is smaller than the observed anomaly by over an order of magnitude,
gravity darkening seems to be an unlikely explanation.

The scenario of transit timing variations (TTVs) producing the
asymmetry seems unlikely because our analysis showed that transit
timing variations in \sn\ have amplitudes smaller than $\approx$10
minutes (see Figure~\ref{fig:obliquity}).  This is consistent with
previous results from \citet{holczer_transit_2016}.  Moreover, the
transit timing variations we do observe are correlated with the local
light curve slope, which on average increases as much as it decreases.
From our analysis, the mean TTV and its standard deviation are
$0.00\pm12.05$ minutes; similarly the mean local slope and its
standard deviation are $0.49\pm44.49$\,ppt\,day$^{-1}$.  There is
therefore no expectation for TTVs to produce the asymmetry.
